WGS fastq2vcf walkthrough

### 2023-03-22 index02.Rmd
menu mod
added panel seminars to index02

# Panel Seminars 
To facilitate discussions about practices and pitfalls in applying 'omics to non-model systems, we hosted [Q & A panel seminars](ADMIN_03_panels.html) with experts on topics ranging from RADseq, population genomics with WGS, and transcriptomics. Check them out on [YouTube](https://www.youtube.com/channel/UCosG6JfIj7k0DizfsD5ADfQ)!

# How to contribute!
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates, technicians, and faculty members. A diverse range of perspectives and backgrounds will make these tutorials more inclusive, informative, and useful for everyone in the marine-omics community. If you are interested in developing an information page or tutorial for the website,  we ask that you review our [page with instructions for submitting content](ADMIN_01_submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).

>>>>

# Panel Seminars

To facilitate discussions about practices and pitfalls in applying 'omics to non-model systems, we hosted Q & A panel seminars with experts on topics ranging from RADseq, population genomics with WGS, and transcriptomics in May-June 2021. 3-5 expert panelists discussed each topic, with questions coming from the working group and the audience. Videos are available on YouTube!

| Date        | Topic       | Panelists     | Video     |
| :---        | :---        | :---          | :---      |
| May 7         | GBS/RADseq genotyping pipelines     | [Melanie LaCava](https://melanielacava.weebly.com/), [Alicia Mastretta-Yanes](http://mastrettayanes-lab.org/), [Isaac Overcast](https://isaacovercast.github.io/), [Jon Puritz](https://www.marineevoeco.com/)   | [View video](https://www.youtube.com/watch?v=C74GBESeIq4)     |
| May 21       |  WGS genotyping (low and high coverage)     | [Jeffrey Good](http://www.thegoodlab.org/), [Mikhail "Misha" Matz](https://matzlab.weebly.com/), [Noah Reid](http://nreid.github.io/), [Tim Sackton](https://scholar.harvard.edu/tsackton), [Nina Overgaard Therkildsen](https://www.therkildsenlab.com/) | [View Video](https://www.youtube.com/watch?v=ObJ3OT3dwSw)    |
| June 4       |  Population genomic analyses and filtering data     | [Zach Gompert](https://gompertlab.com/), [Morgan Kelly](http://www.morgankelly.biology.lsu.edu/), [Katie Lotterhos](https://sites.google.com/site/katielotterhos/home), [Jeff Ross-Ibarra](https://rilab.ucdavis.edu/) |  [View Video](https://youtu.be/dZyuqVEGPMo)   |
| June 18       |  RNAseq (experimental design through differential expression)     | [Ana Conesa](http://conesalab.org/), [Sarah Davies](http://sites.bu.edu/davieslab/), [Martin Hölzer](https://hoelzer-lab.github.io/), [Joanna Kelley](https://labs.wsu.edu/genomes/), [Harold Pimentel](https://pimentellab.com/)     |  [View Video](https://youtu.be/-gQ59m2cck0)   |

# How to Contribute
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates, technicians, and faculty members. A diverse range of perspectives and backgrounds will make these tutorials more inclusive, informative, and useful for everyone in the marine-omics community. If you are interested in developing an information page or tutorial for the website, we ask that you review our [page with instructions for submitting content](ADMIN_01_submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).
